### 2016-08-17 rebuttal.tex

\end{solution}

\question Lines 359 and 379: what is 2D text representation? It seems that ``2D'' shouldn't be here.
\begin{solution}

\end{solution}

\question Line 427: every dictionary is a ``dictionary of keys''. This should be a dictionary with coordinate tuples as keys associated with the appropriate values.
\begin{solution}
``Dictionary of Keys'' (DOK) refers specifically to a sparse matrix
representation where entries are stored as \texttt{(row, column)} pairs
mapping to the elements. See for instance \texttt{scipy.sparse.dok\_sparse}. We
have fixed the capitalization of ``Dictionary of Keys'' and added the
abbreviation (DOK), and stated explicitly what is meant by this. We have also
made a similar note about List of Lists (LIL) earlier in the section.
\end{solution}

### 2016-08-17 matrices.tex
Reinstate "dictionary of keys" and clarify some things
See also this discussion from GitHub
https://github.com/sympy/sympy-paper/pull/144#discussion_r63944359

Besides being an important feature in its own right, computations on
matrices with symbolic entries are important for many algorithms
within SymPy.  The following code shows some basic usage of the
\texttt{Matrix} class.
\begin{verbatim}
>>> A = Matrix(2, 2, [x, x + y, y, x])
>>> A
Matrix([
[x, x + y],
[y,     x]])
\end{verbatim}

@@

Internally these matrices store the elements as lists of lists, making
it a dense representation.\footnote{Similar to the polynomials module, dense
  here means that all entries are stored in memory, contrasted with a sparse
  representation where only nonzero entries are stored.} For storing sparse
matrices, the \verb|SparseMatrix| class can be used.

>>>>

Besides being an important feature in its own right, computations on
matrices with symbolic entries are important for many algorithms
within SymPy.  The following code shows some basic usage of the
\texttt{Matrix} class.
\begin{verbatim}
>>> A = Matrix([[x, x + y], [y, x]])
>>> A
Matrix([
[x, x + y],
[y,     x]])
\end{verbatim}

@@

Internally these matrices store the elements as Lists of Lists (LIL), meaning
the matrix is stored as a list of lists of entries (effectively, the
input format used to create the matrix \texttt{A} above), making it a
dense representation.\footnote{Similar to the polynomials module, dense here
  means that all entries are stored in memory, contrasted with a sparse
  representation where only nonzero entries are stored.} For storing sparse
matrices, the \verb|SparseMatrix| class can be used. Sparse matrices store
their elements in Dictionary of Keys (DOK) format, meaning entries are stored
as \texttt{(row, column)} pairs mapping to the elements.
